Donations' tax in Chile

### 2020-08-05 README.Rmd
ETL reference

- [article-elsevier.Rmd](article-elsevier/article-elsevier.Rmd): generates the manuscript
  - [mybibfile.bib](article-elsevier/mybibfile.bib): contains the database of references
- [presentation.Rmd](presentation/presentation.Rmd): reproduces a presentation of the article

>>>>

- [article-elsevier.Rmd](article-elsevier/article-elsevier.Rmd): generates the manuscript
  - [ETL.R]() prepares the data used in the article
  - [mybibfile.bib](article-elsevier/mybibfile.bib): contains the database of references
- [presentation.Rmd](presentation/presentation.Rmd): reproduces a presentation of the article
